Founder allele effects for hotspot traits

### 2019-09-17 analysis/paper/Rmd/hotspot-one-chromosome.Rmd
updated README

```{r, scols-peak-position-{{hot_chr}}}

binning <- local_nonlocal_annot %>%
  dplyr::select(symbol, pos, lod) %>%
  mutate(bin = unlist(pos) %>%
           map(.f = function(x) {x %>% 
               bin_peak_position(breaks = hot_lower + (1:9) * 0.4) %>%
               binarize_bin_number(total_number_of_bins = 10L)
             })
  ) %>%
  listcol_to_cols(list_column = quo(bin), another_column = quo(symbol))
```

@@

```{r, prepare-annotations-{{hot_chr}}}
# need 5 annotation object: 1. local v nonlocal, 2. mediation LOD difference for all local traits, 3. mediation LOD difference proportion for all local traits, 4. 8 allele effects per trait, 5. peak position per trait, encoded as binned position
# 2,3,4 are numeric; 1 & 5 are binary
## local_nonlocal_annot already has the allele effect and local v nonlocal; binning has the peak position. Need to join these two on symbol
### med_tib has lod diff & lod diff proportion for all local - nonlocal pairs
fake_tibble_mediation <- tidyr::crossing(symbol = local_annot2$symbol, 
                                         symbol2 = local_annot2$symbol) %>%
  mutate(dat = NA) %>%
  spread(key = symbol, value = dat) %>%
  rename(symbol = symbol2)
# to add to mediation tibbles

@@

```{r, define-contrasts-{{hot_chr}}}
contrasts_BC_FG <- local_nonlocal_annot %>%
  ungroup() %>%
  select(symbol, cA:cH, local_tx, lod) %>%
  mutate(row_num = 1:nrow(local_nonlocal_annot), 
         AB = abs(cA - cB),
         AC = abs(cA - cC),
         AD = abs(cA - cD),
         AE = abs(cA - cE),
         AF = abs(cA - cF),
         AG = abs(cA - cG),
         AH = abs(cA - cH),
         BC = abs(cB - cC),
         BD = abs(cB - cD),
         BE = abs(cB - cE),
         BF = abs(cB - cF),
         BG = abs(cB - cG),
         BH = abs(cB - cH),
         CD = abs(cC - cD),
         CE = abs(cC - cE),
         CF = abs(cC - cF),
         CG = abs(cC - cG),
         CH = abs(cC - cH),
         DE = abs(cD - cE),
         DF = abs(cD - cF),
         DG = abs(cD - cG),
         DH = abs(cD - cH),
         EF = abs(cE - cF),
         EG = abs(cE - cG),
         EH = abs(cE - cH),
         FG = abs(cF - cG),
         FH = abs(cF - cH),
         GH = abs(cG - cH)
  ) %>%
  mutate(BC_A = abs((cB + cC) / 2 - cA),
         BC_D = abs((cB + cC) / 2 - cD),
         BC_E = abs((cB + cC) / 2 - cE),
         BC_F = abs((cB + cC) / 2 - cF),
         BC_G = abs((cB + cC) / 2 - cG),
         BC_H = abs((cB + cC) / 2 - cH),
         BC_FG = abs((cB + cC) - (cF + cG))
         ) %>%
  select(symbol, BC_FG)
```

@@

>>>>

@@

```{r, prepare-annotations-{{hot_chr}}}
# need 5 annotation object: 1. local v nonlocal, 2. mediation LOD difference for all local traits, 3. mediation LOD difference proportion for all local traits, 4. 8 allele effects per trait, 5. peak position per trait, as a one-column heatmap
# 2,3,4 are numeric; 1 & 5 are binary
## local_nonlocal_annot already has the allele effect and local v nonlocal; binning has the peak position. Need to join these two on symbol
### med_tib has lod diff & lod diff proportion for all local - nonlocal pairs
fake_tibble_mediation <- tidyr::crossing(symbol = local_annot2$symbol, 
                                         symbol2 = local_annot2$symbol) %>%
  mutate(dat = NA) %>%
  spread(key = symbol, value = dat) %>%
  rename(symbol = symbol2)
# to add to mediation tibbles

@@

@@

### Allele effects contrasts

```{r, define-submap-{{hot_chr}}}
figdir <- here::here("analysis", "figures", "Chr{{hot_chr}}-allele-effects-plots")
names(s1coef_out) -> ids # need to run inline code above to define s1coef_out
# find indices on Chr5 for boundaries of hotspot
which(map[[hot_chr]] > hot_lower)[1] -> start_index
which(map[[hot_chr]] > hot_upper)[1] -> stop_index
submap <- list()
submap$`5` <- map[[hot_chr]][start_index:stop_index]
mylist <- list()
for (i in 1:(nlocal + nnonlocal)) {
  mylist[[i]] <- s1out[ , i, drop = FALSE]
}
```

```{r effects-plots-{{hot_chr}}}
purrr::pmap(.l = list(s1coef_out, as.list(ids), mylist), 
           .f = function(x, y, z){
             main <- local_nonlocal_annot %>%
               ungroup() %>%
               filter(annot.id == y) %>%
               select(annot.id, symbol) %>%
               paste0()
             fn <- here::here("analysis", "figures", "Chr{{hot_chr}}-allele-effects", paste0(main, ".pdf"))
             pdf(file = fn)
             qtl2::plot_coefCC(x, map = submap, main = main, scan1_output = z)
             dev.off()
           }
)

```

## Barplots for effects at peak positions

Now, let's focus only on the 8 values at the LOD peak for each trait.

```{r, barplots-scan1coef-effects-{{hot_chr}}, fig.height = 20, fig.width = 8}
ord2 <- match(table = local_nonlocal_annot$symbol, x = rn)
foobar <- local_nonlocal_annot %>%
  select(symbol, cA:cH) %>%
  (function(x) x[ord2, ]) %>%
  tidyr::gather(key = "founder_allele", value = "effect", cA:cH)
foobar2 <- arrange(transform(foobar,
             symbol = factor(symbol, levels = rn)), symbol)
foobar2 %>% 
  ggplot() + geom_col(aes(y = effect, x = founder_allele, fill = founder_allele)) +
  ylim(c(-1.5, 1.5)) + 
  facet_wrap(symbol ~ ., ncol = 4) #+ theme(strip.text.x = element_blank())
ggsave(here::here("analysis", "figures", "allele_effects_at_peaks-{{hot_chr}}.png"), limitsize = FALSE)
```

### 2019-09-17 analysis/paper/preliminary/allele-effects-exploration.Rmd
updated README

```{r setup_continued}
hot_chr <- c(2, 5, 7, 11, 13)
hot_mid <- c(165.5, 146, 46, 71, 112.5)
keller_mediator <- c("Hnf4a", "Pdx1", "Fam83e", "Sat2", "Il6st")
inputs <- tibble(hot_chr, hot_mid, keller_mediator)
out <- pmap_dfc(inputs, .f = function(hot_chr, hot_mid, keller_mediator) knitr::knit_expand(text = readLines(here::here("analysis", "paper", "Rmd", "hotspot-one-chromosome.Rmd"))))
# note that ... argument must be a list, ie, it must be a single argument, not multiple args
```

@@

```{r, define-submap}
figdir <- here::here("analysis", "figures", "Chr5-allele-effects-plots")
names(s1coef_out) -> ids # need to run inline code above to define s1coef_out
# find indices on Chr5 for boundaries of hotspot
which(map$`5` > hot_lower)[1] -> start_index
which(map$`5` > hot_upper)[1] -> stop_index
submap <- list()
submap$`5` <- map$`5`[start_index:stop_index]
mylist <- list()
for (i in 1:203){
  mylist[[i]] <- s1out[ , i, drop = FALSE]
}
```

```{r effects-plots}
purrr::pmap(.l = list(s1coef_out, as.list(ids), mylist), 
           .f = function(x, y, z){
             main <- local_nonlocal_annot %>%
               ungroup() %>%
               filter(annot.id == y) %>%
               select(annot.id, symbol) %>%
               paste0()
             qtl2::plot_coefCC(x, map = submap, main = main, scan1_output = z)
           }
)
```

## Barplots for effects at peak positions

Now, let's focus only on the 8 values at the LOD peak for each trait.

```{r, barplots-scan1coef-effects, fig.height = 20, fig.width = 8}
ord2 <- match(table = local_nonlocal_annot$symbol, x = rn)
foobar <- local_nonlocal_annot %>%
  select(symbol, cA:cH) %>%
  (function(x) x[ord2, ]) %>%
  tidyr::gather(key = "founder_allele", value = "effect", cA: cH)
foobar2 <- arrange(transform(foobar,
             symbol=factor(symbol,levels=rn)),symbol)
foobar2 %>% 
  ggplot() + geom_col(aes(y = effect, x = founder_allele, fill = founder_allele)) +
  ylim(c(-1.5, 1.5)) + 
  facet_wrap(symbol ~ ., ncol = 4) #+ theme(strip.text.x = element_blank())
ggsave(here::here("analysis", "figures", "allele_blupss_at_peaks.png"), limitsize = FALSE)
```

@@

>>>>

```{r setup_continued}
hot_chr <- c(2, 5, 7, 11, 13)
hot_mid <- c(165.5, 146, 46, 71, 112.5)
keller_mediator <- c("Hnf4a", "Pdx1", "Fam83e", "Sat2", "Il6st")
inputs <- tibble(hot_chr, hot_mid, keller_mediator)
out <- pmap_dfc(inputs, .f = function(hot_chr, hot_mid, keller_mediator) knitr::knit_expand(text = readLines(here::here("analysis", "paper", "Rmd", "hotspot-one-chromosome.Rmd"))))
# note that ... argument for knit_expand must be a list, ie, it must be a single argument, not multiple args
```

@@

@@

What if more than one contrast is "responsible" for a given block in a hotspot? Maybe max of two contrasts, for example? Or min of two contrasts?
